\chapter{Introduction}\label{C:intro}
This chapter gives an introduction to the project report.

Software is embedded into our daily lives. From ensuring that a plane remains airborne to helping doctors administer treatment. With these critical systems, testing needs to be used to ensure functional correctness and error free. Without correct testing, incidents can occur resulting in serious injury and death. A notable example is the Therac-25 where patients were dosed with sometimes thousands of times the greater than normal amount of radiation. 

\section{Motivation}
\todo{Motivation}

\section{Approach}

During a tests execution, it leaves a 'paper trail' behind. This trail is the method executions that are called within the test, referred to as the tests spectrum. \todo{Picture?.} This spectrum will be the set of data that will be analysed through different algorithms to determine how related a test is with another. \todo{More}

\section{Aim}

The aim of the project is to identify different approaches that give the developers an idea on the number of redundant test cases that are contained within a project. It should allow the developer to run a set of pipelines they specify and view the test cases on a GUI, allowing manual inspection to determine if they are truly redundant. This means that the tool is useful for gaining an overview and understanding of the condition of the current test suite. A potential use of the tool is to allow for splitting of the somewhat redundant tests into one seperate test suites, each run at different times.
